Network Cascades

### 2016-08-25 paper/paper.tex
Tease readers about the explanation to the cumulative distributions graph
Interpret Watts' figure 2

A node is vulnerable if its threshold is low enough so that only one of its neighbors needs to switch state for it to switch state itslef. Such nodes can be thought of as ``early adopters'' of a technology, with the initial seed beeing an ``innovator''. A vulerable cluster is a connected set of nodes that all switch state if a contained ``early adopter'' adjacent to an ``innovator'' switches its state. This cluster must span a sufficiently (Watts never explicitly states what ``sufficient'' in this case means) large portion of the network (percolate) for the cascade condition to be true.

@@

@@

>>>>

A node is vulnerable if its threshold is low enough so that only one of its neighbors needs to switch state for it to switch state itslef. Such nodes can be thought of as ``early adopters'' of a technology, with the initial seed beeing an ``innovator''. A vulerable cluster is a connected set of nodes that are ``early adopters'' (that are vulnerable) adjacent to an ``innovator''. This cluster must span a sufficiently (Watts never explicitly states what ``sufficient'' in this case means) large portion of the network (percolate) for the cascade condition to be true.

@@

Further insights on the cascade window can be gained by examining the size of cascades around its boundaries. Figure \ref{fig:cascade-size} shows the cumulative distribution of the cascade sizes. The size of a cascade is measured in terms of the ratio between agents in state $1$ to the total number of agents. The examinded section of the window is the same as in figure \ref{fig:cross-section}. See \ref{sec:findings} for Watts' interpretation of this graph.

@@

In the above section \ref{fig:cross-section} was introduced as a means to compare the properties of the cascade window for a given threshold. Watts' interpretation of the results is as follows:

There is an obvious relation of the frequency of global cascades (open circles, in the middle) to the relative size of the vulnerable cluster (long dashes and crosses, the lower two graphs). They are roughly proportional, but the size of the cluster ``underestimates'' the cascade frequency. The given explanation for this is, that agents directly adjacent do the vulnerable cluster (who are themselves not vulnerable) can still trigger further cascades or promote the expansion of a cascade in the latter state of the cascade when most of it's vulnerable neighbors have been switched. This explanation is validated by examining the size of the extended vulnerable cluster, which comprises the vulnerable cluster plus its immediate (stable) neighbor nodes. And indeed the plot for the extended vulnerable cluster (short dashes, in the middle) is virtually equal to the cascade frequency, thus validating the explanation.

The average size of global cascades (solid line and solid circles, the upper graphs) is obviously not related to the size of the vulnerable cluster or the extended vulnerable cluster, since it does not decline with decreasing sizes for greater values of $z$. It is only governed by the $z$, i.e. the connectivity of the whole network. The raltionship between connectivity and cascade size is further examined below, using figure \ref{fig:cascade-size}. The intuition that with decresing size of the vulnerable cluster (to which the cascade is limited) the size of cascades should also decrease is false. Although unable to give a defititive explanation, Watts tries to explain this phenomenon: In the later stages of the cascade, the cascade has switched a lot of vulnerable nodes to $1$. In this situation it is possible that stable nodes, i.e. nodes that need more than one neighbor switching to switch themselves, have multiple switched adjacent vulnerable nodes and now do switch. This process could repeat itself until the entire connected component to which the vlunerable cluster belongs might be switched. Watts did not investigate in this paper if this phenomenon only occurs in the examinded class of random graphs or if it also appears in other random graphs.
